---
title: "Agricultural Drilldown on Kiva Loans Using Reticulate"
output:
  html_document:
    toc: true
---

I've already gained some familiarity with this data from building a Shiny app
for mapping it, but I want to take this opportunity to also brush up my Python
and use reticulate to smoothly integrate with R.

For this specific notebook, I'm going to take a closer look at agricultural loans
and see what we can learn about them. I already did some initial data cleaning and
manipulation in R for the map, so I'm going to reuse that element.

```{r setup, echo=TRUE, message=FALSE, error=FALSE, warning=FALSE}
library(reticulate)
library(magrittr)
library(dplyr)
use_condaenv("py3")

knitr::knit_engines$set(python = reticulate::eng_python)

source("kiva_loan_cleaning.R")

```

After pulling in the data initially from my existing R script, now I'm calling it into python
 and converting it to a pandas df for continuing along.
```{python, echo=TRUE}
import pandas as pd
loanspd = pd.DataFrame(r.loans)

print(loanspd.head(n=5))
```
Looks like what I'm expecting, great. 

## By Country
Now let's start digging up some insights. What proportion of all loans are agricultural, on a country by country basis?
```{python, echo=TRUE}
import numpy as np

loanspd['Agriculture'] =  np.where(loanspd['sector']=="Agriculture", True, False)
print(loanspd.head(n=5))

```

```{python, echo=TRUE}
agloan = loanspd[loanspd['Agriculture'] == True]
bycountry = agloan.groupby(['country', 'Agriculture']) 
sumcountry = bycountry['usd_amt'].describe()
print(sumcountry.head(n=5))

```
I discovered that I can't make R handle a pandas summary object directly, so this summary work I did in python
has to be done in R. Not a big deal, I'm sure I'll figure out how to coerce a summary
 object sometime later!
 
### Table - Top 20 Countries
 
```{r}

ag_df <- py$agloan %>%
  group_by(country, Agriculture) %>%
  summarize(mean_loan = mean(usd_amt, na.rm = T)
            , median_loan = median(usd_amt, na.rm = T)
            , min_loan = min(usd_amt, na.rm = T)
            , max_loan = max(usd_amt, na.rm=T)
            , n())

ag_df <- ag_df %>%
  ungroup() %>%
  top_n(20, wt=median_loan)

knitr::kable(ag_df)

```


### Plot - Top 20 Countries
```{r, fig.height=20}
library(ggplot2)
ag_df$country <- factor(ag_df$country, levels = ag_df$country[order(ag_df$median_loan)])

ggplot(ag_df, aes(x=country, group = country, y= median_loan))+
  theme(legend.position="none")+
  geom_bar(aes(fill = country), position = "dodge", stat="identity")+
  coord_flip()+
  labs(title="Top 20 Countries by Median Agricultural Loan Amount (USD)")
```



## References

Because I am using this as both a project and a learning exercise, I'm including 
the best results from my inevitable google searches here.

 * http://bconnelly.net/2013/10/summarizing-data-in-python-with-pandas/   
 * https://rstudio.github.io/reticulate/articles/r_markdown.html#calling-r-from-python  
 * https://chrisalbon.com/python/data_wrangling/pandas_selecting_rows_on_conditions/   

